The Analog Method for Precipitation Prediction: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-11-24 Moving temporal window - HESS/template.tex
Updating the discussion on the use of an old reanalysis dataset.

The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution. Newer reanalysis dataset could have been used to achieve this study, and might have resulted in higher performance scores. However, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset, especially if the information of the atmospheric circulation is more accurate. Indeed, a better dataset does not negatively influence the fact that one can find better analog situations at other hours of the day rather than at fixed hours. A comparative analysis of several reanalysis dataset within the AM is under work and will be the topic of a dedicated paper.

%TODO: : it was shown by some studies that the resolution of the reanalysis dataset does not improve significantly the performance of the analogy of the atmospheric circulation. However, a full analysis of this aspect is out of the scope of this publication, and is a topic we are working on right now. Nevertheless, we can make the assumption that it does not alter the fact that we can find better analog situations at different hours of the day.

>>>>

The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution. Newer reanalysis dataset could have been used to achieve this study, and might have resulted in higher performance scores. However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small. This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution. That might not be the case of more elaborated methods relying on thermodynamic data. A comparative analysis of several reanalysis dataset within the AM is under work and will be the topic of a dedicated paper.

Moreover, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset. Indeed, a better dataset does not negatively influence the fact that one can find better analog situations at other hours of the day rather than at fixed hours.
